Report

### 2020-12-23 report.Rmd
Compute l, ld, gini, fish-fish network, temporal network, species trends

- Species richness:
  - decreases a lot in time when biomass decreases
  - increases slightly in time when biomass increases

@@

@@

- Richness:
  - when biomass increases, competitive interactions may prevent the increase in
    species richness.
  - when biomass decreases conjointly to species richness, it may reflect...
    haaaa: difficult because we do not know if the chicken or the egg was first.
  - Implication for conservation: looks easiest to loose species than gain them.

- Avg trophic level: 
  - Higest trophic level concentrates most of the biomass, so gain and loss are
    statistically more linked to them

@@

@@

```{r pred-other-com}
plot_signif <- pred_plot_signif %>%
  filter(!variable %in% get_com_str_var())
legend_signif <- get_legend(
  plot_signif$myplot[[1]] +
    theme(legend.position = "bottom")
)
plot_signif$myplot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = plot_signif$myplot,
  labels = plot_signif$variable
)
plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r}
pred_plot_signif %>%
  select(variable, data) %>%
  unnest(data) %>%
  ggplot() %>%
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error, xmax = bm_slope +
      bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3)
  }
  ggplot()
plot_final_model
```

>>>>

- Species richness:
  - decreases a lot in time when biomass decreases
  - increases slightly in time when biomass increases
  - No effect of community size! (same for the number of nodes)

@@

- Connectance:
  - do not decrease when biomass decreases in little communities
  - decreases when biomass decreases in big communities
  - do not vary when biomass increases

- Weighted connectance:
  - increases when biomass decreases in little communities
  - decreases when biomass decreases in big communities
  - decreases when biomass increases

@@

- Richness:
  - When biomass increases, one can that species richness increases as well
    as when biomass decreases conjointly to species richness.
  - Increase in species richness necessitates colonization events, i.e.
    stochastic events while decreases in species richness necessitates
    disparition of species already in the community. Thus, the colonization
    process
  - second explanation: when biomass increases, competitive interactions may prevent the increase in
    species richness. We expect that processes based on competition would raise
    the role of community size.

- Avg trophic level: 
  - Higest trophic level concentrates most of the biomass, so gain and loss are
    statistically more linked to them
  - In biggest communities, there was no link between biomass and avg trophic
    level dyn because those communities already contain high trophic
    levels (There is a positive correlation between the number of pisc node and
    biomass of the community). So, there is a saturation at the top of the
    chain.
    - The observation that the number of link and link density follow the same
      pattern confirm this interpretation.

- Connectance:
  - In little communities, few piscivorous species and so loss of biomass do not
    change the foodwebs because fish-resource links are quite redondant.
    - there is a positive correlation between nb of pisc node and biomass.
    - In bigger communities, the loss of the highest piscivorous nodes/species
      (see average trophic level), which have a lot of interactions, leads to a
      decrease of connectance over time.
  - Increase in biomass was weakly related to an increase in node number or species
    richness, so it is not surprising that connectance to not vary.

- Weighted connectance:
  - When biomass decreases in little communities, loss of highest trophic level
    and so less big predators and weighted connectance become more even
    - In big communities, the highest number can make the absence of such an effect 
  - When Biomass increases, the number of predator nodes increases (especially
    in little communities), and ...
    the biomass

The key to understand the difference between little and big communities is the
number of piscivorous nodes.

@@

### Further analysis

```{r}
loadd(summary_var_f3y)

summary_var_f3y %>%
  na.omit() %>%
  select(bm_std, avg_IS, l, ld, m, A, gini, log_bm_std, connectance, log_rich_std, rich_std, w_trph_lvl_avg,
    weighted_connectance, nbnode_std, nb_pisc_node_std, prop_pisc_node) %>%
  cor() %>%
  corrplot::corrplot(corr = .)

summary_var_f3y %>%
  ggplot(aes(x = bm_std, y = prop_pisc_node)) +
  geom_point() 
#summary_var_f3y %>%
  #ggplot(aes(x = log_bm_std, y = nb_pisc_node_std))+
  #geom_point() 
#summary_var_f3y %>%
  #ggplot(aes(x = , y = nb_pisc_node_std))+
  #geom_point() 
```

@@

```{r pred-other-com, fig.dim = c(12, 10)}
plot_signif <- pred_plot_signif %>%
  filter(!variable %in% get_com_str_var())
legend_signif <- get_legend(
  plot_signif$myplot[[1]] +
    theme(legend.position = "bottom")
)
plot_signif$myplot %<>% map(., ~.x + theme(legend.position = "none"))
top_signif_other <- plot_grid(
  plotlist = plot_signif$myplot,
  labels = plot_signif$variable
)
plot_grid(top_signif_other, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r eval = FALSE}
pred_plot_signif %>%
  select(variable, data) %>%
  unnest(data) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = bm)) +
  geom_errorbar(
    aes(xmin = bm_slope - bm_slope_strd_error, xmax = bm_slope +
      bm_slope_strd_error), alpha = .3) +
  geom_errorbar(
    aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error),
    alpha = .3)
```

```{r}
loadd(log_bm_net_group_f3y)
st_id_plot <- log_bm_net_group_f3y %>%
  filter(variable %in% get_com_str_var()) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  scale_color_viridis() +
  geom_text(aes(label = station)) +
  facet_wrap(~variable, scales = "free_y")
st_id_plot
st_network_to_plot <- c(513, 1453, 16654, 6020)
```

- Station ploted: `r st_network_to_plot`

```{r}
library(tidygraph)
library(ggraph)
#source(mypath("R", "plot_methods.R"))
myload(network_analysis,
  envir = environment(),
  dir = get_mypath("data", "classes"))
myload(op_analysis,
  metaweb_analysis,
  envir = environment(),
  dir = get_mypath("data"))
meta <- metaweb_analysis; rm(metaweb_analysis)
st_sp_node <- network_analysis %>%
  select(opcod, composition) %>%
  left_join(dplyr::select(op_analysis, opcod, station, date), by = "opcod") %>%
  unnest(cols = c(composition)) %>%
  group_by(station) %>%
  summarise(
    nbnode = length(unique(sp_class)),
    nbsp = length(unique(str_extract(sp_class, "[A-Z]+")))
  ) %>%
  arrange(nbsp)

net <- network_analysis %>%
  dplyr::select(opcod, network) %>%
  unnest(cols = c(network)) %>%
  left_join(., dplyr::select(op_analysis, opcod, station, date)) %>%
  mutate(date = lubridate::year(date))

myload(species_color_temporal_plot,
  envir = environment(),
  dir = get_mypath("data"))
```

```{r}
#st_id_plot
temporal_network <- map(st_network_to_plot, function (st) {
  net_ex <- filter(net, station == st)
  p <- my_crap_temporal_network(
    net = net_ex,
    metaweb = meta$metaweb,
    network_data = network_analysis,
    nrow_sp_legend = 2,
    return_data = TRUE,
    my_y_lim = c(0, 4.1),
    bm_var = "bm_std",
    color_node = species_color_temporal_plot
  )
  plot_grid(plotlist = p$plots)
  })
temporal_network[[1]]
temporal_network[[2]]
temporal_network[[3]]
temporal_network[[4]]
```

```{r}
loadd(rigal_species)
species_trends <- rigal_species %>%
  unnest(classif) %>%
  select(station, species = variable, linear_slope, linear_slope_strd_error, linear_slope_pvalue)

species_trends2 <- species_trends %>%
  left_join(filter(log_bm_net_group_f3y, variable == "connectance") %>%
    select(station, bm_slope),
    by = "station")
species_trends2 %<>% na.omit

species_trends2 %>%
  filter(linear_slope_pvalue < 0.05) %>%
  ggplot(aes(y = linear_slope, x = bm_slope, color = species)) +
  geom_point()

species_trend_cor <-
  species_trends2 %>%
  group_by(species) %>%
  summarise(
    spear = cor(linear_slope, bm_slope, method = c("spearman"), use = "pairwise.complete.obs"),
    n = n()
  )

species_trend_cor %>%
  filter(n >= 20) %>%
  ggplot(aes(y = spear, x = species)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45))
```

```{r}
# Obtain avg troph lvl by species
dead_material <- c("det", "biof")
tlvl <- NetIndices::TrophInd(meta$metaweb, Dead = dead_material)$TL
names(tlvl) <- colnames(meta$metaweb) 
tlvl <- enframe(tlvl, name = "sp_class", value = "tlvl")

species_tlvl <- 
  tlvl %>%
  filter(str_detect(sp_class, "[A-Z]{3}.")) %>%
  mutate(species = str_sub(sp_class, 1, 3)) %>%
  group_by(species) %>%
  summarise(tlvl = mean(tlvl, na.rm = TRUE))
```

```{r}
species_trend_cor %>%
  left_join(species_tlvl, by = "species") %>%
  filter(n > 20) %>%
  ggplot(aes(x = tlvl, y = spear)) +
  geom_point() +
  geom_smooth(method = "lm")
```
